---
title: "Script Documentation"
author: "Monika"
date: "July 2026"
output: html_document
---

# Purpose

This R script demonstrates a basic data analysis workflow. It imports a dataset, performs simple data cleaning, summarizes the data, and creates basic visualizations. The script is intended for learning purposes and follows R Markdown best practices.

# Inputs

- CSV data file
- R programming language
- Required packages:
  - tidyverse
  - ggplot2

# Outputs

- Cleaned dataset
- Summary statistics
- Basic charts
- HTML report after knitting

# Required Packages

```{r}
library(tidyverse)
library(ggplot2)
```

# Example Code

```{r}
data <- read.csv("data.csv")

head(data)

summary(data)
```

# Notes

- Ensure all required packages are installed.
- Verify the dataset path before running the script.
- Review the output for accuracy.

# Conclusion

This R Markdown document provides clear documentation for an R script, including its purpose, inputs, outputs, and example code. It is designed to improve readability and maintainability.
